Models

### 2022-08-30 analysis/05_model_metrics.Rmd
minor changes to visualizations

Visualize number of years for each timeseries
```{r}
hist_numYears <- metrics %>%
  select(year, rarefyID) %>% 
  distinct() %>% 
  count(rarefyID, name = "num_years") %>% 
  ggplot() +
  geom_histogram(aes(x = num_years),
                 binwidth = 2) +
  scale_x_continuous(name = 'Number of years sampled',
                     breaks = c(2,4,8,16,32,48,64,96)) +
  #scale_y_continuous(breaks = c(0,2500,5000,7500,10000,12500, 15000, 17500, 20000,22500)) +
  labs(tag = 'B',
       y = 'Number of cells') +
  theme_bw() +
  theme(panel.grid.minor.x = element_blank())
```

Visualize distributions of response
```{r}
metrics %>%
  filter(metric %in% c("FRic", "FEve", "FDiv", "FDis", "S", "Jaccard_hind")) %>%
  ggplot() +
  geom_histogram(aes(x = logvalue),
                 bins = 60) +
  facet_wrap(~metric, scales = "free") +
  labs(title = "Distribution of Log values")

metrics %>%
  filter(metric %in% c("FRic", "FEve", "FDiv", "FDis", "S", "SES_FDis", "SES_FDiv", "SES_FEve", "SES_FRic", "Jaccard_hind")) %>%
  ggplot() +
  geom_histogram(aes(x = value),
                 bins = 60) +
  facet_wrap(~metric, scales = "free") +
  labs(title = "Distribution of raw values")
```

>>>>

Visualize number of years for each timeseries
```{r}
hist_numYears <- model_data %>%
  select(year, rarefyID) %>% 
  distinct() %>% 
  count(rarefyID, name = "num_years") %>% 
  ggplot() +
  geom_histogram(aes(x = num_years),
                 binwidth = 2) +
  scale_x_continuous(name = 'Number of years sampled',
                     breaks = c(2,4,8,16,32,48,64,96)) +
  #scale_y_continuous(breaks = c(0,2500,5000,7500,10000,12500, 15000, 17500, 20000,22500)) +
  labs(tag = 'B',
       y = 'Number of cells') +
  theme_bw() +
  theme(panel.grid.minor.x = element_blank())

hist_duration <- model_data %>%
  select(rarefyID, duration) %>% 
  distinct() %>% 
  ggplot() +
  geom_histogram(aes(x = duration),
                 binwidth = 2) +
  scale_x_continuous(name = 'Number of years sampled',
                     breaks = c(2,4,8,16,32,48,64,96)) +
  #scale_y_continuous(breaks = c(0,2500,5000,7500,10000,12500, 15000, 17500, 20000,22500)) +
  labs(tag = 'B',
       y = 'Number of cells') +
  theme_bw() +
  theme(panel.grid.minor.x = element_blank())
```

Visualize distributions of response
```{r}
# metrics %>%
#   filter(metric %in% c("FRic", "FEve", "FDiv", "FDis", "S", "Jaccard_hind")) %>%
#   ggplot() +
#   geom_histogram(aes(x = logvalue),
#                  bins = 60) +
#   facet_wrap(~metric, scales = "free") +
#   labs(title = "Distribution of Log values")
# 
# metrics %>%
#   filter(metric %in% c("FRic", "FEve", "FDiv", "FDis", "S", "SES_FDis", "SES_FDiv", "SES_FEve", "SES_FRic", "Jaccard_hind")) %>%
#   ggplot() +
#   geom_histogram(aes(x = value),
#                  bins = 60) +
#   facet_wrap(~metric, scales = "free") +
#   labs(title = "Distribution of raw values")
```
